Component-based Software Development Framework \\for Embedded IoT Devices（仮）

### 2017-11-13 ipsj/paper.tex
Fix typo

In addition, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to software development.
Currently, most embedded software are programmed in C language.
However, development in C language results in large code size, incurs high costs, and requires significant development time.
In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because it is relatively easy to reuse scripts.

@@

Software developers using TECS can be divided into component designers and application developers.
Component designers define signatures, which are interfaces between cells, and celltypes, which are types of cells.
Using the template code generated from the CDL file in which these are defined, component designers implement the functions and behaviors of the component in C language.
The source code implementing the function of the component is called a celltype code.
Application developers develop applications by using component diagrams and predefined celltype to connect cells with build description.
An application module is generated by compiling and linking the header, the interface code, and the celltype code.

@@

\subsubsection{System Model of mruby on TECS}
The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyontecs}.
Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/mrubyontecs.pdf}
\caption{System model of existing mruby on TECS}
\label{fig:mrubyontecs}
\end{figure}

@@

The memory allocator component connects to as many tFixedSizeMemoryPool as required, as shown in Fig.\ref{fig:tMemoryAllocator}.
tFixedSizeMemoryPool is a componentized kernel object of TOPPERS/ASP3 for allocating and release memory areas of a requested size. 
tFixedSizeMemoryPool components of various sizes are prepared, and an appropriate memory area can be allocated according to the used data size.
On the other hand, all components that need to allocate or deallocate memory, e.g., tTCPInput and tEthernetOutput, connect to the memory allocator component.

@@

TLSF (Two-Level Segregate Fit) memory allocator\cite{par:TLSF}\cite{url:TLSF} is a dynamic memory allocator suitable for the real-time system proposed by M. Masmano et al.
TLSF memory allocator has the following features.
\begin{description}
    \item[Real-time property]\mbox{}\\
        The worst execution time required for allocating and deallocating memory does not depend on the data size.
        TLSF always works with $O(1)$, and it is possible to estimate the response time.
    \item[Fast speed]\mbox{}\\
        In addition to being able to always estimate the worst execution time, TLSF is executed at high speed.
    \item[Efficient memory consumption]\mbox{}\\
        Memory efficiency is improved by suppressing memory fragmentation.
        Various tests have obtained an average fragmentation of less than 15\% and a maximum fragmentation of less than 25\%.
\end{description}

@@

TLSF algorithm classifies memory blocks into two stages and searches for a memory block that is optimal for the requested memory size.
The overview of TLSF algorithm is shown in Fig.\ref{fig:TLSF}.
Consider a case where a request, $malloc(100)$, is called to allocate a memory.
In the first step, it is classified by the most significant bit of the requested memory size.
In this case, since 100 is represented by binary number as 1100100, it is in the range from 64 to 128 from the most significant bit.
In the second step, it is further classified.
In this case, 64 to 128 are divided into 4, and 100 is in the block of 96 to 111.
Free block \footnote{Free block is an available memory block.} in this range is used.

@@

Fig.\ref{src:TLSFSignature} is a signature description for memory management used by the allocator.
It defines the memory pool initialization function {\it initializeMemoryPool}, memory allocation function {\it calloc}, {\it malloc}, {\it realloc}, and memory release function {\it free} as a signatures.

@@

The celltype description of the TLSF memory allocator component is shown in Fig.\ref{src:TLSFCelltype}.
An entry port, {\it eMalloc}, is connected to all components that perform memory management such as $malloc$ and $free$.
Here, {\it [inline]} is a specifier for Implementation as inline functions.
A memory pool size is defined as an attribute, and a pointer to a memory pool is defined as an variable.
Each component holds its own heap area, so even when calling functions for memory management at the same time in different threads, it is possible to operate without memory contention.

@@

Fig.\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component shown in Fig.\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
Two sets of task components and TLSF components are combined.
Each memory pool size can be configured as an variable (Lines 5 and 11 in Fig.\ref{src:TLSFBuild}).
Fig.\ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
The use part shows a function that the mruby VM allocates memory in the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS2} which is introduced in Section \ref{sec:mrubyonTECS}.
Lines 8 calls the {\it free} function of the TLSF memory allocator component.
{\it cMalloc\_} represents the name of the call port (Lines 2 in Fig.\ref{src:TLSFBuild}).
Likewise, Lines 13 and 17 call the function for memory allocation.
The heap area of {\it TLSFMalloc\_001} component is used if the code of \ref{src:TLSFC} is executed in {\it Task\_001}, and if that is executed in {\it Task\_002}, the heap area of {\it TLSFMalloc\_002} component is used, respectively.
In this way, in the component-based development using TECS, it is possible to operate with the same code without modifying the C code, although the cells are different.

>>>>

In addition, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to software development.
Currently, most embedded software is programmed in C language.
However, development in C language results in large code size, incurs high costs, and requires significant development time.
In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because it is relatively easy to reuse scripts.

@@

Software developers using TECS can be divided into component designers and application developers.
Component designers define {\it signature}s, which are interfaces between {\it cell}s, and {\it celltype}s, which are types of {\it cell}s.
Using the template code generated from the CDL file in which these are defined, component designers implement the functions and behaviors of the component in C language.
The source code implementing the function of the component is called a {\it celltype} code.
Application developers develop applications by using component diagrams and predefined {\it celltype} to connect {\it cell}s with build description.
An application module is generated by compiling and linking the header, the interface code, and the {\it celltype} code.

@@

\subsubsection{System Model of mruby on TECS}
The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyonTECS}.
Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/mrubyonTECS.pdf}
\caption{System model of existing mruby on TECS}
\label{fig:mrubyonTECS}
\end{figure}

@@

The memory allocator component connects to as many tFixedSizeMemoryPool as required, as shown in Fig.\ref{fig:tMemoryAllocator}.
tFixedSizeMemoryPool is a componentized kernel object of TOPPERS/ASP3 for allocating and releasing memory areas of a requested size. 
tFixedSizeMemoryPool components of various sizes are prepared, and an appropriate memory area can be allocated according to the used data size.
On the other hand, all components that need to allocate or deallocate memory, e.g., tTCPInput and tEthernetOutput, connect to the memory allocator component.

@@

TLSF (Two-Level Segregate Fit) memory allocator\cite{par:TLSF}\cite{url:TLSF} is a dynamic memory allocator suitable for the real-time system proposed by M. Masmano et al.
TLSF memory allocator has the following features.
\begin{description}
    \item[Real-time property]\mbox{}\\
        The worst execution time required for allocating and deallocating memory does not depend on the data size.
        TLSF always works with $O(1)$, and it is possible to estimate the response time.
    % \item[Fast speed]\mbox{}\\
    %     In addition to being able to always estimate the worst execution time, TLSF is executed at high speed.
    \item[Efficient memory consumption]\mbox{}\\
        Memory efficiency is improved by suppressing memory fragmentation.
        Various tests have obtained an average fragmentation of less than 15\% and a maximum fragmentation of less than 25\%.
\end{description}

@@

TLSF algorithm classifies memory blocks into two stages and searches for a memory block that is optimal for the requested memory size.
The overview of TLSF algorithm is shown in Fig.\ref{fig:TLSF}.
Consider a case where a request, $malloc(100)$, is called to allocate a memory.
In the first step, it is classified by the most significant bit of the requested memory size.
In this case, since 100 is represented by binary number as 1100100, it is in the range from 64 to 128 from the most significant bit.
In the second step, it is further classified.
In this case, 64 to 128 are divided into 4, and 100 is in the block of 96 to 111.
Free block\footnote{Free block is an available memory block.} in this range is used.

@@

Fig.\ref{src:TLSFSignature} is a signature description for memory management used by the allocator.
It defines the memory pool initialization function {\it initializeMemoryPool}, memory allocation function {\it calloc}, {\it malloc}, {\it realloc}, and memory release function {\it free} as a signature.

@@

The celltype description of the TLSF memory allocator component is shown in Fig.\ref{src:TLSFCelltype}.
An entry port, {\it eMalloc}, is connected to all components that perform memory management such as $malloc$ and $free$.
Here, {\it [inline]} is a specifier for Implementation as inline functions.
A memory pool size is defined as an attribute, and a pointer to a memory pool is defined as a variable.
Each component holds its own heap area, so even when calling functions for memory management at the same time in different threads, it is possible to operate without memory contention.

@@

Fig.\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component shown in Fig.\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
Two sets of task components and TLSF components are combined.
Each memory pool size can be configured as a variable (Line 5 and 11 in Fig.\ref{src:TLSFBuild}).
Fig.\ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
The use part shows a function that the mruby VM allocates memory in the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS2} which is introduced in Section \ref{sec:mrubyonTECS}.
Line 8 calls the {\it free} function of the TLSF memory allocator component.
{\it cMalloc\_} represents the name of the call port (Line 2 in Fig.\ref{src:TLSFBuild}).
Likewise, Line 13 and 17 call the function for memory allocation.
The heap area of {\it TLSFMalloc\_001} component is used if the code of \ref{src:TLSFC} is executed in {\it Task\_001}, and if that is executed in {\it Task\_002}, the heap area of {\it TLSFMalloc\_002} component is used, respectively.
In this way, in the component-based development using TECS, it is possible to operate with the same code without modifying the C code, although the cells are different.
